### 2018-10-10 Chapters/Chapter1.tex
commit before fix

Antiferromagnetism was first studied by L. N\'eel who introduced a thermodinamic theory that made it possible to explain the antiferromagnetic order and it pretict the existance of a temperature above which this order vanishes. This temperature is known as N\'eel temperature. In the next section we will present a semiclassical model for antiferromagnetic materials.

>>>>

Antiferromagnetism was first studied by L. N\'eel who introduced a thermodynamic theory following the Weiss's model of a local molecular field. This made it possible to explain the antiferromagnetic order and it predicted the existence of a temperature above which this order vanishes. This temperature is known as N\'eel temperature. Later N\'eel proposed the picture of a magnetic order where two sublattices were magnetised in opposite directions. During the same period, Lev Landau developed a phenomenological model using a combination of two antiferromagnetically coupled ferromagnetic layers.

### 2018-10-10 Chapters/Chapter2.tex
Fixes
commit before fix

The Bloch function is extended over the whole crystal volume $V$. We would like to work with a localized basis. An alternative orthonormal basis are the Wannier functions $\ket{\psi_{n\bs{k}}}$, defined in terms of the Bloch functions as:

\begin{align}
\bra{\bs{r}}\ket{\phi_{in}} &= \frac{1}{\sqrt{M}}\sum_{\textbf{k}\in BZ} e^{-i\textbf{k}\textbf{r}_i} \bra{\bs{r}}\ket{\psi_{n\textbf{k}}} \label{Wannier1} \\
\bra{\bs{r}}\ket{\psi_{n\bs{k}}} &= \frac{1}{\sqrt{M}} \sum_{\bs{R}} e^{i\bs{k}\bs{R}} \bra{\bs{r}}\ket{\phi_{\bs{R}n}} \label{Wannier2}
\end{align}

Where $M$ is the number of lattice sites as defined in \ref{AP1A}. Using \ref{Bloch1} we see that $\phi_{in}(\textbf{r}) = \phi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \phi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations. From now on we will restrict ourselves to a fixed band, so we will drop the band index. Additionally, we will include the spin state, therefore the basis states will have two quantum numbers one for the site and one for the spin state. We will adopt the notation $\ket{i\sigma}$ for the basis state of site $i$ with spin state $\sigma = \uparrow, \downarrow$, or just $\ket{i}$ when the spin state is irrelevant. Fock space states with small number of particles will be denoted as $\ket{i\sigma, j\sigma'}$, for a state with a particle at site $i$ with spin $\sigma$ and a particle at $j$ with spin $\sigma'$, or $\ket{ij}$ when spin is irrelevant.

@@

>>>>

The Bloch function is extended over the whole crystal volume $V$. We would like to work with a localized basis. An alternative orthonormal basis are the Wannier functions $\ket{\psi_{in}}$, defined in terms of the Bloch functions as:

\begin{align}
\bra{\bs{r}}\ket{\phi_{n\bs{k}}} &= \frac{1}{\sqrt{M}}\sum_{\bs{R}} e^{i\bs{k}\bs{R}} \bra{\bs{r}}\ket{\psi_{\bs{R}n}}  \label{Wannier1} \\
\bra{\bs{r}}\ket{\psi_{in}} &= \frac{1}{\sqrt{M}} \sum_{\bs{k}\in BZ} e^{-i\textbf{k}\textbf{R}_i} \bra{\bs{r}}\ket{\phi_{n\bs{k}}}\label{Wannier2}
\end{align}

Where $M$ is the number of lattice sites as defined in \ref{AP1A}. Using \ref{Bloch1} we see that $\psi_{in}(\textbf{r}) = \psi_{0n}(\textbf{r}-\textbf{r}_i) \equiv \psi_{n}(\textbf{r}-\textbf{r}_i)$, so we only need to define one Wannier function for each band and the others are obtained by translations. From now on we will restrict ourselves to a fixed band, so we will drop the band index. Additionally, we will include the spin state, therefore the basis states will have two quantum numbers one for the site and one for the spin state. We will adopt the notation $\ket{i\sigma}$ for the basis state of site $i$ with spin state $\sigma = \uparrow, \downarrow$, or just $\ket{i}$ when the spin state is irrelevant. Fock space states with small number of particles will be denoted as $\ket{i\sigma, j\sigma'}$, for a state with a particle at site $i$ with spin $\sigma$ and a particle at $j$ with spin $\sigma'$, or $\ket{ij}$ when spin is irrelevant.

@@

Compare with \cite{Stepanov2017}.

### 2018-10-10 Chapters/Chapter3.tex
commit before fix

\end{section}
\end{subappendices}

>>>>

\begin{section}{Identities}

Let $Z(t)$ be an operator dependent on the parameter $t$. Then:

\begin{align*}
d_t e^{Z} &= d_t \sum_{n=0}^\infty \frac{1}{n!} Z^n = \sum_{n=0}^\infty \sum_{m=0}^{n-1} \frac{1}{n!} Z^m \frac{\partial Z}{\partial t} Z^{n-m-1} = \\
&= \sum_{m=0}^\infty \sum_{p=0}^\infty \frac{1}{(m+p+1)!}Z^m \frac{\partial Z}{\partial t} Z^p = \sum_{m=0}^\infty \sum_{p=0}^\infty \frac{m!p!}{(m+p+1)!} \frac{Z^m}{m!} \frac{\partial Z}{\partial t} \frac{Z^p}{p!} =\\
&= \sum_{m=0}^\infty \sum_{p=0}^\infty \int_0^1 dx x^m (1-x)^p \frac{Z^m}{m!} \frac{\partial Z}{\partial t} \frac{Z^p}{p!} = \int_0^1 dx e^{Zx} \frac{\partial Z}{\partial t} e^{Z(1-x)} = \\
&= \int_0^1 dx \sum_{n=0}^\infty \frac{1}{n!} \left[xZ, \dots, \left[xZ, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z
\end{align*}

Where we used the Beta function $\int_0^1 dx x^m (1-x)^p = \frac{m!p!}{(m+p+1)!}$ and we also used the Baker–Campbell–Hausdorff expansion for $e^{xZ}\frac{\partial Z}{\partial t}e^{-xZ}$ and $\int_0^1 x^n = \frac{1}{n+1}$. Therefore we proved:

\begin{equation}
d_t e^{Z} = \sum_{n=0}^\infty \frac{1}{(n+1)!} \left[Z, \dots, \left[Z, \frac{\partial Z}{\partial t}\right] \dots \right] e^Z
\end{equation}

\end{subappendices}
